%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% LaTeX sources for The Guide to Software Engineering & Professional Practice
%% Michael B. Gale (m.gale@bham.ac.uk)
%%
%% This work is licensed under the Creative Commons
%% Attribution-NonCommercial-NoDerivatives 4.0 International License. To
%% view a copy of this license, visit
%% http://creativecommons.org/licenses/by-nc-nd/4.0/ or send a letter to
%% Creative Commons, PO Box 1866, Mountain View, CA 94042, USA.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{\sshFullName}

Smart home technology is increasingly popular in homes throughout the UK. \sshFullName\ is a start-up which specialises in producing hardware and software specifically aimed at student houses. The products are marketed either directly at students or providers of student accommodation. For students to be able to use the products, they must be suitable for use in rented accommodation. In other words, they must not require any permanent modifications to the accommodation. In either case, the products must be suitable for multiple users, who may not have the same level of trust for each other as members of the same family.

Some of their existing products are outlined in the following sections.

\subsubsection{The \sshHub}

The \emph{\sshHub} is \sshShortName' most recent smart home hub product. The device is USB-powered and connects other \ssh\ products in the student home (via Bluetooth or WiFi) to the \sshCloud\ (via WiFi). It runs software which detect \ssh\ products in range, communicates with them, and propagates information between the \sshCloud\ and those devices.

\subsubsection{The \sshCloud}

The \emph{\sshCloud} encompasses all of \sshFullName' online services. It includes both a web-based interface that users can access to manage their accounts and remote-control their devices, as well as services that exchange information with the \sshHubShort s.

\subsubsection*{The \sshApp}

The \emph{\sshApp} is an iOS and Android app which allows users to access and control their \ssh\ devices from their smartphones. The \sshApp\ communicates with the \sshCloud, which in turn communicates with the user's \sshHub, which in turn communicates with the \ssh\ devices.

\subsubsection{The \sshCamera}

The \emph{\sshCamera} is a smart camera which can be positioned almost anywhere thanks to versatile mounting options, including a roll of sticky tape that comes included for free in the box. The camera can be used for multiple different scenarios thanks to its AI features:

\begin{itemize}
    \item By pointing the \sshCamera\ at the front door, it can detect who enters and leaves the student house. The \sshConsole\ (sold separately) will then show a beautiful overview of who is or has been in the house and when.
    \item By pointing the \sshCamera\ at the sink, it can detect who just dumps their dirty dishes in it and never washes up. The \sshCloud\ (subscription required) will then automatically send notifications to the \sshApp\ to remind those house mates to clean up.
    \item By pointing the \sshCamera\ at the fridge, it can detect who takes what from the fridge. The \sshCloud\ (subscription required) will then automatically bill users for items they have taken, but weren't theirs.
\end{itemize}

\subsubsection{The \sshConsole}

The \emph{\sshConsole}\ is a console table made out of beautiful walnut veneer with a touch screen as the table's top surface. The screen allows multiple users to connect to their \ssh\ accounts via an \sshHub\ (sold separately) and provides a central point for students to access the \ssh\ ecosystem in their home. Aside from controlling \ssh\ devices, such as the \sshCamera, the \sshConsole\ allows students:

\begin{itemize}
    \item To view a unified timetable to help plan joint events
    \item To see who is currently in the house and when people have come and gone
    \item Arrange rotas, such as for who cleans the dishes or takes out the bins
    \item View rankings for who has washed the most dishes or washed them the fastest (\sshCamera\ required, sold separately)
    \item Make purchases from third-party providers and automatically split the bill
\end{itemize}
